---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lazyseq

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The package `lazyseq` implements a lazy version of `base::list`. All elements are only evaluated when they are needed. E.g. when you convert the `lazy_list` to a normal `list` or when you access a single element.

All very experimental.

## Installation

``` r
remotes::install_github("dirkschumacher/lazyseq")
```

## Example

This is a basic example:

```{r example}
library(lazyseq)
content <- 42
ll <- lazy_list(
  (function() {print("eval"); 1})(), 
  (function() !!content)(), 
  stop("will never be executed")
)
ll
ll[[1]]
ll[[2]]
as.list(ll[-3])
```


## Contribute

Feel free to contribute. Ideally post an issue first or ping me on Twitter, but all contributions are welcome.

## Code of Conduct

Please note that the lazyseq project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
